On g~0~

### 2017-03-22 manuscript.Rmd
updated Lopez data

```{r echo=FALSE}
includefigs <- FALSE
library(png)
library(grid)

@@

**Figure 7**. Minimum conductance measured from leaf dry-down curves on a variety *Hakea* species, a genus native to Australia. Plants were grown in containers in a grow house, and supplied with ample water or underwent long-term mild drought stress. Bars are labelled by leaf form : broadleaf (B) or needle-like (N). g~min~ was higher for species with needle-like leaves, both for well-watered plants (Wilcoxon test, p `r pval(wilcox.test(gmin.w ~ leaf.form, data=lopw)$p.value)`) and droughted plants (p `r pval(wilcox.test(gmin.d ~ leaf.form, data=lopw)$p.value)`).

>>>>

```{r echo=FALSE}
includefigs <- TRUE
library(png)
library(grid)

@@

**Figure 7**. Minimum conductance measured from leaf dry-down curves on a variety *Hakea* species, a genus native to Australia. Plants were grown in containers in a grow house, and supplied with ample water or underwent long-term mild drought stress. Bars are labelled by leaf form : broadleaf (B) or needle-like (N). For droughted plants, g~min~ was higher for species with needle-like leaves (Wilcoxon test, p `r pval(wilcox.test(gmin.d ~ leaf.form, data=lopw)$p.value)`)), but not for well-watered plants (p `r pval(wilcox.test(gmin.w ~ leaf.form, data=lopw)$p.value)`).
